Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells

### 2019-05-14 Paper/paper.tex
Reworded paragraph of DFT methods

DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid oxides in bulk or slab form.
Calculations were performed using the pseudo--potentials from the PSlibrary with scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
A value of 75.0 Ry was used for the kinetic energy cutoff, which were tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV per atom.
Monkhorst-Pack k-point sampling of the Brillouin zone was chosen to be $4\times4\times4$ for most calculations using cells of approximately 5.5 \AA $\times$ 7.6 \AA $\times$ 5.5 \AA, due to the variable size of the cells after variable cell relaxation.
The k-point grid used was also tested using the same criterion to ensure convergence.

>>>>

DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid structures in bulk or slab form.
These calculations were performed using the pseudo--potentials from the PSlibrary including scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
A value of 75.0 Ry was used for the kinetic energy cutoff, which was tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV was obtained per atom.
Monkhorst-Pack k-point sampling of the Brillouin zone was chosen to be $4\times4\times4$ for most calculations.
The criterion used involved using a k-point grid of 4 on the edge of a cell between 5 and 8 \AA in length, then to preserve the grid on bigger or smaller cells, the grid was scaled accordingly.
The k-point grids used were also tested using the same criterion from energy converge to ensure convergence with respect to grid size.
